Uncertainty on the galaxy-halo connection for Lyman-$\alpha$ emitters at $z=3.1$

### 2016-06-14 paper/ms.tex
new references

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig,ulem}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}

@@

% To highlight comments 
\definecolor{red}{rgb}{1,0.0,0.0}
\newcommand{\red}{\color{red}}
\definecolor{darkgreen}{rgb}{0.0,0.5,0.0}
\newcommand{\SRK}[1]{\textcolor{darkgreen}{\bf SRK: \textit{#1}}}
\newcommand{\SRKED}[1]{\textcolor{darkgreen}{\bf #1}}
\newcommand{\before}[1]{\textcolor{red}{ #1}}
\newcommand{\after}[1]{\textcolor{darkgreen}{ #1}}

@@

\begin{abstract}
 In this paper we study the impact of cosmic variance and observational uncertainties
in constraining the mass and occupation fraction, \focc, of
dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
To this end, we constructed mock catalogs from an N-body simulation to match the 
typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
In our model a dark matter halo with mass in the range $\mmin
<M_{\mathrm h}<\mmax$ can only host one detectable LAE at most.    
We proceed to  explore the parameter space determined by \mmin, \mmax\ and \focc\
with a Markov Chain Monte-Carlo algorithm using the angular correlation function (ACF) and the LAEs number density  as observational constraints. 
We find that the preferred minimum and maximum masses in our model span
a wide range $10^{10.0}\hMsun\leq \mmin \leq 10^{11.1}\hMsun$ ,
$10^{11.0}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
As a consequence the median mass, $M_{50}$, of all the consistent models has a large uncertainty $M_{50} =
3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.
However, we find that the same individual models have a relatively tight
$1\sigma$  scatter around the median mass $\Delta M_{1\sigma} = 0.55^{+0.11}_{-0.31}$ dex.
We are also able to show that \focc\ is uniquely determined by $M_{\rm
  min}$, regardless of $M_{\rm max}$. 
We argue that upcoming large surveys covering at least $25$ deg$^{2}$
should be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
distribution width, $W_{1\sigma}$, constructed over several fields of
$\sim 1$ deg$^{2}$.
These results suggest that taking explicitly into account the effect of cosmic
variance using cosmological simulations is a valuable tool to 
interpret LAEs observations at high redshift.
\end{abstract}

@@

Fig. \ref{fig:like} shows an interesting feature for \mmin. 
The histogram (upper left) showing the probability for this parameter
given the observational constraints does not considerably decreases for lower
masses. 
A valid questions is the following. Down to which values of
\mmin\ does the probability significantly decreases?

@@

@ARTICLE{2004ApJ...600L.171S,
   author = {{Somerville}, R.~S. and {Lee}, K. and {Ferguson}, H.~C. and 
	{Gardner}, J.~P. and {Moustakas}, L.~A. and {Giavalisco}, M.
	},
    title = "{Cosmic Variance in the Great Observatories Origins Deep Survey}",
  journal = {\apjl},
   eprint = {astro-ph/0309071},
 keywords = {Galaxies: Statistics, Cosmology: Large-Scale Structure of Universe},
     year = 2004,
    month = jan,
   volume = 600,
    pages = {L171-L174},
      doi = {10.1086/378628},
   adsurl = {http://adsabs.harvard.edu/abs/2004ApJ...600L.171S},
  adsnote = {Provided by the SAO/NASA Astrophysics Data System}
}

>>>>

\documentclass{emulateapj}
\submitted{{\it Submitted for publication in ApJ}}
\usepackage{multirow,color,wrapfig}
\usepackage {graphicx}
\usepackage{graphics}
\usepackage[dvips]{epsfig}

@@

% To highlight comments

@@

\begin{abstract}
 In this paper we study the impact of cosmic variance and observational uncertainties
in constraining the mass and occupation fraction, \focc, of
dark matter halos hosting \ly\ Emitting  Galaxies (LAEs) at high redshift. 
To this end, we construct mock catalogs from an N-body simulation to match the 
typical size of observed fields at $z=3.1$ ($\sim 1 {\rm deg^2}$).
In our model a dark matter halo with mass in the range $\mmin
<M_{\mathrm h}<\mmax$ can only host one detectable LAE at most.    
We proceed to  explore the parameter space determined by \mmin, \mmax\ and \focc\
with a Markov Chain Monte-Carlo algorithm using the angular correlation function (ACF) and the LAEs number density  as observational constraints. 
We find that the preferred minimum and maximum masses in our model span
a wide range $10^{10.0}\hMsun\leq \mmin \leq 10^{11.1}\hMsun$ ,
$10^{11.0}\hMsun\leq \mmax \leq 10^{13.0}\hMsun$; followed by a
wide range in the occupation fraction $0.02\leq \focc \leq 0.30$.   
As a consequence the median mass, $M_{50}$, of all the consistent models has a large uncertainty $M_{50} =
3.16^{+9.34}_{-2.37}\times 10^{10}$\hMsun.
However, we find that the same individual models have a relatively tight
$1\sigma$  scatter around the median mass $\Delta M_{1\sigma} = 0.55^{+0.11}_{-0.31}$ dex.
We are also able to show that \focc\ is uniquely determined by $M_{\rm
  min}$, regardless of $M_{\rm max}$. 
We argue that upcoming large surveys covering at least $25$ deg$^{2}$
should be able to put tighter constraints on \mmin\ and \focc\ through the LAE number density
distribution width, $W_{1\sigma}$, constructed over several fields of
$\sim 1$ deg$^{2}$.
These results suggest that taking explicitly into account the effect of cosmic
variance using cosmological simulations is a valuable tool to 
interpret LAEs observations at high redshift.
\end{abstract}

@@

Fig. \ref{fig:like} shows an interesting feature for \mmin. 
The histogram (upper left) showing the probability for this parameter
given the observational constraints does not considerably decreases for lower
masses. 
This raises the following question. Down to which values of
\mmin\ does the probability significantly decreases?

@@
